Synthesizing Symmetric Lenses

### 2018-07-09 papers/SymmetricLenses/main.tex
Couple quick reactions

In contrast to the identity lens, the \Disconnect lens does not propagate edits
from one format to the other. The disconnect lens takes four arguments: two
regular expressions and two strings. The regular expressions specify the formats
of the corresponding data on the two sides while the strings provide default
values. On creates, the input values are thrown away, and default values are
returned ($\CreateROf{\String} =
\lstinline{"UNK"}$), and on puts, the second argument is used, and the first is
thrown away ($\PutROf{\String}{\StringAlt} = \StringAlt$). In our extended
example, the \lstinline{salary} and \lstinline{company} fields are independent,
so we use the disconnect lens to relate them\bcp{Potentially confusing to
  readers (and, even to me, hacky). Why not relate each of them to the constant
  empty string?}\afm{I'm fine with the empty string.  I've seen sentinel values
  like UNK used before in practice, but if it makes the example cleaner and more
  comprehensible, sure.  Anybody else have thoughts on the matter?}.
The defaults are strings that indicate the information is missing.
%
\begin{lstlisting}
disconnect(salary, company, "unk", "UNK") : salary $\Leftrightarrow$ company
\end{lstlisting}
%
The insert \lstinline{ins} and delete \lstinline{del} lenses are
syntactic sugar for uses of the disconnect lens in which a string
constant is omitted entirely from the source and target formats,
respectively.
\begin{lstlisting}
 ins($t$) = disconnect("", $t$, "", $t$)
 del($s$) = disconnect($s$, "", $s$, "")
\end{lstlisting}

@@

We now provide the typing derivations and semantics for these lenses. For
simplicity of presentation,\bcp{Is there any known issue with relaxing this
  restriction? I've often found ti convenient to use id lenses with ambiguous
  REs...}\afm{no known issues, I just didn't want to go into specifics about
  ambiguity in an already-full paper}, we define the typing derivations and
semantics only over unambiguous regular expressions, even though some lenses can
be defined over ambiguous regular expressions (for example, the identity lens
doesn't need any ambiguity constraints).

>>>>

In contrast to the identity lens, the \Disconnect lens does not propagate edits
from one format to the other. The disconnect lens takes four arguments: two
regular expressions and two strings. The regular expressions specify the formats
of the corresponding data on the two sides while the strings provide default
values. On creates, the input values are thrown away, and default values are
returned ($\CreateROf{\String} =
\lstinline{"UNK"}$), and on puts, the second argument is used, and the first is
thrown away ($\PutROf{\String}{\StringAlt} = \StringAlt$). In our extended
example, the \lstinline{salary} and \lstinline{company} fields are independent,
so we use the disconnect lens to relate them\bcp{Potentially confusing to
  readers (and, even to me, hacky). Why not relate each of them to the constant
  empty string?}\afm{I'm fine with the empty string.  I've seen sentinel values
  like UNK used before in practice, but if it makes the example cleaner and more
  comprehensible, sure.  Anybody else have thoughts on the matter?}\bcp{No,
  I meant why not concatenate two disconnect lenses, one relating salary to
  the empty string and one relating the empty string to company.}.
The defaults are strings that indicate the information is missing.
%
\begin{lstlisting}
disconnect(salary, company, "unk", "UNK") : salary $\Leftrightarrow$ company
\end{lstlisting}
%
The insert \lstinline{ins} and delete \lstinline{del} lenses are
syntactic sugar for uses of the disconnect lens in which a string
constant is omitted entirely from the source and target formats,
respectively.
\begin{lstlisting}
 ins($t$) = disconnect("", $t$, "", $t$)
 del($s$) = disconnect($s$, "", $s$, "")
\end{lstlisting}

@@

We now provide the typing derivations and semantics for these lenses. For
simplicity of presentation,\bcp{Is there any known issue with relaxing this
  restriction? I've often found ti convenient to use id lenses with ambiguous
  REs...}\afm{no known issues, I just didn't want to go into specifics about
  ambiguity in an already-full paper}\bcp{OK, we can just comment that we
  believe relaxing this restriction is unproblematic.}, we define the typing derivations and
semantics only over unambiguous regular expressions, even though some lenses can
be defined over ambiguous regular expressions (for example, the identity lens
doesn't need any ambiguity constraints).
